The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Tr\"aff and Francesco Versaci, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}

### 2014-02-14 article/article.tex
abstract

\maketitle
\begin{abstract}

\end{abstract}

>>>>

\maketitle
\begin{abstract}
Balls-into-bins is a classical allocation problem, where $m$ balls have to be distributed among $n$ bins as evenly as possible. Using ranomized allocations schemes, the placement algorithm does not need to know the current load of all bins when the next ball has to be allocated. A classical and well studied approach is to select a bin uniformly and independently at random for each ball. Another strategy is to select $d\geq 2$ bins for each ball and put the ball into the bin with the least load. Somewhat surprisingly, the maximum load achieved by such a multiple-choice scheme is significantly smaller, even for $d=2$. In this paper, we will present two different multiple-choice allocation strategies for the balls-into-bins problem and provide a detailed analysis for the upper bounds on the maximum load that they achieve. We will use a technique called witness trees that has proven useful in a wide variaty of balls-into-bins problems.
\end{abstract}
